Lemma 1

### 2021-03-08 notes/jessie-russian-lemma.tex
Fixing up lemma statement

As measurable functions are closed under (countable) intersections, we can simply show $Q_z$ intersection of measurable functions; namely, since we have $Q_z(\omega) = \V_u \cap f: \omega \mapsto \partial L(u,\omega) \cap g : \omega \mapsto \{c : \inprod{z}{c} = L'(u,\omega;z)\}$.

$\V_u$ is measurable by construction as it is a collection of measurable sets.
Moreover, the function $f$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}.
Now, we aim to show the function $g$ is measurable, which follows from measurability of $L'$ and the fact $\inprod{z}{\cdot}$ is continuous in its second argument, hence Borel, the set is measurable. \jessie{Copying Russian argument}

@@

$g(\omega) = \{c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\}$.
For all closed $U \in \reals^d$, have $g^{-1}(U) = \{\omega : \exists c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\} \in \B(\Omega)$

>>>>

As measurable functions are closed under (countable) intersections, we can simply show $Q_z$ intersection of measurable functions; namely, since we have $Q_z(\omega) = \V_u \cap f: \omega \mapsto \partial L(u,\omega) \cap g : \omega \mapsto \{c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\}$.

$\V_u$ is measurable by construction as it is a collection of measurable sets.
Moreover, the function $f$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}.
Now, we aim to show the function $g$ is measurable, which follows from measurability of $L'$ and the fact $\inprod{z}{\cdot}$ is continuous in its second argument, hence Borel, the set is measurable. \jessiet{Copying Russian argument}

@@

%\jessie{Notes to self; ignore}
%$g(\omega) = \{c \in \reals^d : \inprod{z}{c} = L'(u,\omega;z)\}$.
%For all closed $U \in \reals^d$, have $\{\omega : \{c: \inprod{z}{c} = L'(u,\omega;z)\} \cap U \neq \emptyset\} \in \B(\Omega)$
